\large{\bf Large effects and the infinitesimal model }

### 2023-12-02 review-responses.tex

\noindent
{\bf To the Editor(s) -- }

\vskip 1em

We are writing to submit a revision of our manuscript, ETCETERA

In particular, please note that
we provide a copy of the paper with both highlighted changes
and hyperlinked reviewer comments.

@@

\reply{
    We agree that \citet{turelli2017commentary} is clear about when the Gaussian emerges.
    It also seems quite clear to us that what we say in this paragraph agrees
    with \citet{turelli2017commentary}, who says in his Abstract that
    \begin{quote}
    This commentary distinguishes three nested approximations, referred to as “infinitesimal genetics,” “Gaussian descendants” and “Gaussian population,” each plausibly called “the infinitesimal model.” 
    \end{quote} 
    We think that the underlying issue here may be about motivation for the section.
    To make the motivation, and the point about the Gaussian population assumption more clear,
    we've added some explanatory text \revref.
    Also note that this section does \emph{not} make a Gaussian-population (or, non-Gaussian population) assumption;
    to make this more clear we've changed the phrase later in this paragraph
    from ``non-Gaussian model'' to ``model with non-Gaussian Mendelian sampling terms''.
}

\begin{point}{}
More generally, I found it a bit hard to follow the overall logical flow of section 4.1, especially once the authors launch into an exploration of the ``reproduction'' and ``noise'' terms (pages 9 and 10).
    It would be useful to clarify what the biological/intuitive meaning of the noise and reproduction terms at the outset. It would also be useful to state (at the beginning) what the main goal of these explorations is: (is the goal to identify when both terms ``have well-posed limits independent of the other'' as stated at \llname{limit_remark}), and also to summarise (at the end) to what extent one can do this in all generality.
\end{point}

\reply{
    Good suggestion; we've added more clarifying points;
    see \llname{clarification1}
    and \llname{clarification2}
    (and \llname{clarification3}).
}

@@

\begin{point}{}
    Discussion: In the context of theory combining large and small-effect loci, \citet{chevin2008selective}: ``Selective Sweep at a Quantitative Trait Locus in the Presence of Background Genetic Variation'' and \citet{lande1983response}: ``The response to selection on major and minor mutations affecting a metrical trait'' may also be somewhat relevant.
\end{point}

\reply{
    Thanks! We've incorporated these \revref.
}

%%%%%%%%%%%%%%
\reviewersection{2}

\begin{quote}
The authors investigate the possibility of extending results of \citet{barton2017infinitesimal} on et al (2017) on the
justification of the infinitesimal model to distributions of effect sizes with a large tail (i.e.,
polynomial decay with exponent $\alpha < 2$). This is biologically interesting and important
because there are clear indications that variation in some traits is caused by a mixture
of polygenic (infinitesimal) contributions and one or few loci of large effect. It also a
mathematically difficult topic because it leads into the realm of generalized Central Limit
Theorems, namely stable laws.

@@

After a brief, partly rough (see detailed comments below) introduction the ms starts with
a statistical analysis of the effect size distributions of a large number of traits (all human
disease related) for which GWAS data are available. The evaluation shows that almost
all estimated tail exponents are between 1 and 2.5 with a quite flat distribution between
about 1.3 and 2 (some potential statistical artifacts are noted). However, the authors do
not discuss the influence of selection, which could be essential because the traits are disease
related.
\end{quote}

Thanks for the close reading.
We didn't discuss selection here because the question of whether selection contributes
to the distribution of segregating allelic effects
is somewhat orthogonal to the question at hand here:
in other words, the infinitesimal model describes (an approximation for)
the \emph{results of} random reassortment (etcetera) of whatever ancestral variation is present,
and is therefore relatively agnostic to how that ancestral variation got there.
This works because the infinitesimal model describes trait variation after reproduction
but before selection.
Note that, for instance, there is no obstacle to there being a correlation between effect sizes and allele frequencies,
as one might expect under selection.
However, we have added some clarification about this --
see \revreffull{1}{3} and \llname{discussion_DFEs}.

\begin{quote}
In Section 3, the authors show a kind of negative result concerning the possibility of $\alpha$-stable 
distributions with $\alpha < 2$ (Proposition 1): If the deviations of the offspring trait
from the midparent value (here called the Mendelian sampling term, $R$) are independent
of the midparent value $\bar Z$ (part of the core result in \citet{barton2017infinitesimal}), then the joint
distribution of $R$ and $\bar Z$ is Gaussian. Thus, this independence is not compatible with ‘$\alpha$-stable 
laws’. In fact, as they show (by example) and discuss more generally in Sect. 4, a
single polymorphic large-effect locus causes dependence of $R$ and $\bar Z$.
\end{quote}

We'd like to remind the reviewer of the caveat that this result
also depends on a bit more -- independence of inherited and non-inherited contributions
(e.g., as under an additive model of unlinked loci).

\begin{quote}
In Section 4, a version of the infinitesimal model is investigated that proposes a much
stronger result than a Gaussian Mendelian sampling term independent of the parental
trait distribution, namely a Gaussian distribution of the trait (within the population)
under mutation-selection balance. Although such a model has occasionally been assumed
in the literature, it has never been justified rigorously and, presumably, is not justifiable
(on the basis of realistic assumptions – as clearly noted by Turelli’s brief review and
previous extensive work by Turelli, Barton, and others). Nevertheless, the analysis of the
authors is interesting from a theoretical point of view because they investigate whether
such deterministic mutation-selection balance is possible in a non-Gaussian model that
retains independence of the Mendelian sampling terms, and if such a model might yield a
reasonable approximation to an additive model with non-Gaussian effects.
\end{quote}

We're glad the reviewer liked this section,
but perhaps our introduction to the section was misleading --
in fact we do \emph{not} assume a Gaussian population distribution,
or any population distribution.
Instead, we \emph{ask} which distributions might be population distributions
under this generalized model,
using arguments similar to those found in the literature.
We've tried to make this more clear -- see additional text at \revreffull{1}{8}
and \llname{clarification3}
(and our response to Reviewer 1, point 8).

\begin{quote}
The authors use a simplistic Moran model to investigate these questions. However, mutation 
doesn’t seem to be modeled explicitly. Is it mutation if a parent is replaced by an
offspring of the type described in the display equation at \llname{offspring_eqn}?
Maybe yes, but not necessarily because of segregation and recombination contribute substantially to $R$.
Doesn’t the present assumption imply that the mutation rate is one and that mutation is modeled as a
kind of diffusion? In the latter case, a Gaussian distribution can result. With explicit
mutation models, where mutations occur per locus and a finite number of loci determines the
trait additively, a Gaussian distribution never results (and in no known limit; see above).
How does population size enter? Is this a deterministic Moran model?
\end{quote}

Mutation would enter into $R$, a point we now make \llname{mutation_note},
but without detail, as we are aiming here for a high-level and quick calculation,
not a detailed investigation.
In fact, we thought a bit about how to set up an explicit genotype-to-phenotype map
in which the Mendelian sampling terms are non-Gaussian and independent of parental traits,
but did not arrive at a concrete solution --
we think this is probably possible,
but as we know from Proposition~\ref{prop:parental_contribs},
cannot be a simple additive model.
Investigating how exactly a concrete model of mutation would affect things is beyond the scope of this paper.

\begin{quote}
Anyway, the results
in Sect 4 are of interest because they strongly constrain the possibilities to justify such
‘Gaussian-population approximation’ by any infinitesimal-like model (essentially to
mixtures of Cauchy distributions. The noted relation to blending inheritance is intriguing!).
My main concern is that especially this section needs are clearer description of the model,
and clear distinction between this ‘maximalist’ model (which has little theoretical
support) and the model investigated by Barton et al (2017). Also a much clearer summary
and discussion of the implications of the results shown here are needed. It should not be
assumed that readers have read Turelli (2017) and even less that they have studied
\citet{barton2017infinitesimal} in considerable detail!
\end{quote}

Thanks for the suggestions.
We also thought the section was useful (and also intruiging!),
which is why we left the section in.
(Also note it motivates the form of selection in our simulations.)
We share the reviewer's concern about context,
and have added some additional text
while trying not to get into the weeds too much
-- in particular, see the new text around \llname{clarification3}.

\begin{quote}
In Section 5, it is pointed out why the Barton et al. (2017) fails in the case of ‘Cauchy
noise’ (and presumably for any other limit law with $\alpha < 2$). In the absence of giving the
estimate in App D in Barton et al, the explanation around \llname{approx_eqn} is difficult to
follow. Please provide their estimate for easier comparison (do not assume that readers
studied Barton et al; assume that they scanned (parts) of it).
\end{quote}

\comment{TODO}

\begin{quote}
Finally, Section 6 presents an insightful comparison of the distributions of trait values
resulting from either Gaussian or Cauchy mutation-effect distributions. This seems to be
an explicit genetic model, but again, what is the mutation rate? Clearly, the mutation
rate determines the variance (or more generally variability) of the population distribution.
Please clarify the model. It also needs to be pointed out clearly that such results seem to
be at variance with all (?) explicit multilocus models that have been studied so far.
\end{quote}

Honestly, we're confused by this comment.
The mutation rate is $10^{-9}$ per bp on a genome of length $10^8$,
as stated at \llname{mutation_rate} -- perhaps the reviewer missed that paragraph?
We're also unclear what exactly is meant by ``at variance with all \ldots models'' --
it's true that no-one else has (probably?) simulated this exact model,
but when it comes to simulations, this is often true?
We're not sure which specific aspects of difference the reviewer has in mind pointing out.

\begin{quote}
In summary, this ms contains several interesting aspects and will deserve publication after
improving the presentation and clarifying a number of issues.
\end{quote}

Thanks! We hope our improvements
have made everything at least somewhat clearer.

@@

\reply{
    No, but as written it was confusing, and we've clarified \revref.
    We chose these values by empirical inspection:
    the lower bound was 20 SNPs so that it was not unduly affected by a few large SNPs,
    and the upper bound as 10\% because we wanted the ``tail'', not the ``bulk''.
    (We also checked that changing these values somewhat didn't affect results.)
}

\begin{point}{\revref}
First line in Sect 3: add ‘as $M \to \infty$’. In the next line, this is first time that $\alpha = 2$ is
mentioned. Clarify earlier that this case is very different from $\alpha < 2$ (maybe already below
the last display eq on p3).
\end{point}

\reply{
    Good idea -- done \revref. (Also see \revreffull{2}{1}.)
}

\begin{point}{\revref}
What means `nearby alleles'? Do you mean physically linked
    loci? Another \llname{loci_polymorphic}: alleles are not polymorphic; loci can be polymorphic.
\end{point}

\reply{
    Good points; both are fixed: \revref{} and \llname{loci_polymorphic}.
}

\begin{point}{}
Sect \ref{sec:abnormal}: As noted above, please describe this model in more detail to distinguish it
from that in \citet{barton2017infinitesimal}, which makes much weaker assumptions. Note that it is
not justifiable except under quite extreme assumptions.
\end{point}

\reply{
    We've added more text to hopefully
    put the reader in the right frame of mind:
    see especially \llname{clarification3}.
}

@@

\reply{Thank you for noticing this.  We have corrected this, and the subsequent indices \revref.
}

\begin{point}{\revref}
p 8, last line: Delete ‘to’
\end{point}

\reply{Done \revref.
}

\begin{point}{}
Around \llname{cauchy_note}: It might be useful to mention earlier that the Cauchy distribution is an archetypical
example for an $\alpha$-stable distribution. The enthusiasm among biologists may be limited
though, because all the empirical trait distributions they find have mean and variance. I
don’t know if there are examples in which the variance grows (significantly) as the sample
size increases. In the last para of Sect 4.1 \revref, please specify ‘one will get convergence’. I
suppose this refers again to $M \to \infty$.
\end{point}

\reply{
    Good suggestion -- we've added the note about the Cauchy \llname{cauchy_note}.
    (We haven't tried to make biologists more enthusiastic, though,
    since we don't know of a situation in which strict blending inheritance seems terribly likely.)
    As for the note about ``one will get convergence'' -- it is as the number of generations increases,
    not as $M \to \infty$ (in fact, $M$ does not enter into this section at all);
    we've rewritten this statement to remind the reader
    about what's going on.
}

@@

\reply{
    \comment{TODO}
}

\begin{point}{\revref}
This discussion is too vague. At least, adding a summary of the main findings
would be appropriate (always noting for which version of the infinitesimal model).
\end{point}

\reply{
    We have added a good bit more discussion, including a summary \revref.
}

\begin{point}{\revref}
Does `Lévy stable distribution’ refer to the family of $\alpha$-stable
distributions? (I don’t think it has not been used before.)
\end{point}

### 2023-12-02 writeup.tex
peter edited through

\comment{ADD TO DISCUSSION, WHICH IS SHORT:
    Make the point that another way to think about distibutions with non-finite variance
    is that there's only a finite number of alleles above any fixed value;
    and also the variance in any finite population will be finite.
    (see reviewer comment, ``all the empirical trait distributions they find have mean and variance'')
    Also discuss comparison to fat-tailed dispersal:
    the question is, what distribution gives us a better model?
    For dispersal, a fat-tailed distribution has in practice finite variance
    but is a better model in that it describes noisiness better;
    here, the analogy is something about polygenicity and noisiness of the process of adaptation.
    If we're modeling non-polygenic (oligogenic) traits then
    why stable as opposed to some other arbitrary distribution?
    Well, the distribution of per-allele effect sizes might not be stable, but CLT tells us that maybe
    stable gives a good approx to the process (as in Gaussian case).
}

@@

We should now discuss what this counter-intuitive result says and does not say.
The proposition says, roughly, that if the parental alleles are unlinked and independently chosen,
and meotic segregation is fair,
then independence of Mendelian sampling term from midparent value
\emph{implies} a joint Gaussian distribution for the two.
We have not assumed anything about the distribution of the trait in the population:
rather, we have showed that any model of this sort
that assumes independence of Mendelian sampling term and midparent value
must also, by logical necessity, have a Gaussian distribution for the two.
In other words,
since models can be easily set up for which the distribution of Mendelian sampling terms
is not Gaussian,
the implication of the proposition
is that for such models, independence of the Mendelian sampling term
is not likely a good assumption. \revpoint{1}{7}
Note that the proof does not depend on independence of the $X_\ell$:
indeed, alleles may be inherited together,
although in practice this would quickly create dependencies between the effects
of alleles at such linked loci. \revpoint{2}{5}
Also note that it is \emph{not} usually true that the components --
for instance, $U_M^{[1]}$ and $U_M^{[2]}$ --
are independent of each other.
Finally, note that although they may not be independent,
the Mendelian sampling term $R_M$ and the midparent value $\bar Z_M$
\emph{are} always uncorrelated, since $Z_M$ and $V_M$ are exchangeable.

@@

%%%%%%%%%%%%%%%%%%%%%%
\section{Abnormal quantitative genetics?}

@@

Concretely, consider a  Moran process where an individual whose trait value is $Z$ dies at rate $\mu(Z)$
and is replaced by the offspring of two randomly chosen individuals,
i.e., a new individual with trait
\begin{align*}
  \frac{Z^{1} +Z^{2}}{2} + R ,
\end{align*}
where $Z^{1}$ and $Z^{2}$ are independent draws from the empirical population distribution
and $R$ is an independent draw from the Mendelian sampling distribution
(independent of $Z^{1}$ and $Z^{2}$, with distribution to be specified). 
Mutation-selection balance demands that that
the distribution of individuals removed by death
and the distribution of individuals added by birth are equal,
\ie that $(Z^{1} +Z^{2})/2 + R$ is equal in distribution
to a $\mu$-weighted choice of $Z$.
% In other words, for all bounded and continuous functions $f$,
% \begin{equation} \label{eqn:MSB_condition}
%     \E\left[ f\left(\frac{Z^{1} +Z^{2}}{2} + R \right) \right] = \frac{\E\left[ f(Z) \mu(Z) \right]}{\E[\mu(Z)]},
% \end{equation}
% where the expectation is with respect to the joint law of the population empirical distribution (the law of $Z$, $Z^{1}$ and $Z^{2}$), and $R$.
% 
% Since the set of functions $\mathcal{S} = \{e^{i \theta x} : \theta \in \R\}$ is separating (see \eg \S 3.4 in \cite{Ethier+Kurtz1986}), it suffices to show that \eqref{eqn:MSB_condition} holds for $f \in \mathcal{S}$, \ie
Taking the characteristic function of both these distributions,
deterministic mutation-selection balance is therefore equivalent to
\begin{align} \label{eqn:MSB_CF}
    \frac{\E\left[ e^{i \theta Z}\mu(Z) \right]}{\E[\mu(Z)]}
    =
    \E\left[ e^{i\theta\left(\frac{Z^{1} +Z^{2}}{2} + R \right)}\right] .
\end{align}
Now, we assumed that $Z^{1}$, $Z^{2}$, and $R$ are independent, so we can write \eqref{eqn:MSB_CF} as 
\begin{align*}
    \frac{\E\left[ e^{i\theta Z} \mu(Z) \right]}{\E[\mu(Z)]} &= \E\left[ e^{i\theta\left(\frac{Z^{1} +Z^{2}}{2} + R \right)}\right]\\
	% &= \E\left[ e^{i\frac{\theta}{2} Z^{1}}e^{i\frac{\theta}{2} Z^{2}}e^{\i\theta R}\right]\\
	&= \E\left[e^{i\frac{\theta}{2} Z^{1}}\right]\E\left[e^{i\frac{\theta}{2} Z^{2}}\right]\E\left[e^{i\theta R}\right]\\
	&= \phi\left(\frac{\theta}{2}\right)^{2} \Phi(\theta),
\end{align*}
where
$ \phi(\theta) = \mathbb{E}\left[e^{i\theta Z^{1}}\right] = \mathbb{E}\left[e^{i\theta Z^{2}}\right] $
and
$ \Phi(\theta) = \mathbb{E}\left[e^{i\theta R}\right] $
are the characteristic functions of $Z^{j}$ and $R$, respectively. 
In what follows, we will explore some non-Gaussian solutions $\phi(\theta)$ to equation \eqref{eqn:MSB_CF}:

@@

Since $\varphi(\theta)$ is a characteristic function, it has the Hermitian property: $\phi(-\theta) = \overline{\phi(\theta)}$, and thus $\psi(-\theta) = \overline{\psi(\theta)}$ and $\alpha(-\theta) = \overline{\alpha(\theta)}$.  In particular, if one (and by extension both) limits exist, we must have $\alpha'(0-) = \overline{\alpha'(0+)}$.  In this case, setting $-\gamma + i m = \alpha'(0+)$, we have
\[
	\alpha(\theta) = \begin{cases} 
		i m\theta - \gamma \theta & \text{if $\theta \geq 0$, and}\\
		i m\theta + \gamma \theta & \text{if $\theta < 0$}.
	\end{cases}
\]
If $\gamma > 0$, then we recognize $e^{\psi(\theta)} = e^{im \theta -\gamma|\theta|}$ as the characteristic function of a Cauchy distribution with median 0 and median absolute deviation $\gamma$, whereas if $\gamma = 0$, then $e^{\psi(\theta)} = e^{im \theta}$ is the Fourier transform of a Dirac mass at $m$, \ie the characteristic function for a monomorphic population with all individuals having trait value equal to $m$.

% This might seem a bit roundabout, but the point is that we can prove that $e^{\psi(\theta)}$ is -- in this case -- a characteristic function, so we don't need to lose generality by assuming that it is one.  Our goal is to ask when $\lim_{n \to \infty} \varphi\left(\frac{\theta}{2^{n}}\right)^{2^{n}}\prod_{k=0}^{n-1}\Phi\left(\frac{\theta}{2^{k}}\right)^{2^{k}}$ is a valid characteristic function, and to see what it can be.  
To exclude the case $\gamma < 0$, we first observe that if, as we assume, $\varphi(\theta)$ is the characteristic function of some random variable, say $X$, then $\varphi_{n}(\theta) = \varphi\left(\frac{\theta}{2^{n}}\right)^{2^{n}} = e^{2^{n}\psi\left(\frac{\theta}{2^{n}}\right)}$ is the characteristic function of $2^{-n} \sum_{i = 1}^{2^{n}} X_{i}$, where $X_{1},\ldots,X_{2^{n}}$ are i.i.d. copies of $X$; now, L\'evy's continuity theorem (see \eg Theorem 2.3.4 in \cite{Durrett2005}) tells us that if (i) $\phi_{n}(\theta)$ has a point-wise limit, say $\phi_{\infty}(\theta)$, and (ii) $\phi_{\infty}(\theta)$ is continuous at 0, then $\phi_{\infty}(\theta)$ is the characteristic function of \emph{some} random variable; in particular, if $\alpha(\theta)$ exists and is bounded (\eg if the left and right-hand side derivatives exist, as above), then $\psi(\theta) = \alpha(\theta)\theta$ is continuous at 0, and hence so is $e^{\psi(\theta)}$.  Thus, in this case $e^{\psi(\theta)}$ is itself a characteristic function.  Moreover, being a characteristic function, $e^{\psi(\theta)}$ must satisfy $|e^{\psi(\theta)}| = e^{\Re \psi(\theta)} \leq 1$, whence $\gamma \geq 0$.

@@

More generally, one will get convergence if the noise is a mixture of components with finite variance and stable laws as above, whereas the population distribution will be a mixture of a (possibly degenerate) Cauchy distribution and such noise terms. Note that in the presence of noise, a pure Cauchy-distributed solution is \emph{not} possible in the neutral case.

@@

\section{The difficulty with an abnormal quantitative genetics}

@@

%%%%%%%%%%%%%%%%%%%%%%
\section{Simulations}

In simulation we can easily include realistic recombination (instead of unlinked loci) and selection.
We used SLiM v4 \citep{haller2022slim4}
to simulate a discrete-time approximation to the continuous-time Moran model described above
as follows.
Individuals are diploid, hermaphroditic, and sexual;
the genome is of length $10^8$bp with a uniform recombination rate of $10^{-8}$ crossovers per bp;
mutations occur at a rate of $10^{-9}$ per bp.
Each new mutation is independently assigned an ``effect''
drawn from the ``effect size distribution'' (and will be either Gaussian or Cauchy).
The trait of each individual is determined additively
by summing the effects of all mutations they carry across both chromosomes.
Let $\mu(z)$ be the death rate of an individual with trait $z$,
and let $dt$ be a small constant (we took $dt=0.01$).
In all plots, one time unit is approximately one generation.
Then, at each time step
each individual dies with probability $1 - \exp(-dt \mu(z))$;
if there are $k$ such individuals chosen to die in a given time step,
then we choose $k$ individuals uniformly and without replacement
to produce new offspring;
for each such reproduction event the parent chooses a mate uniformly at random from the population.
This maintains the population at a fixed size, $N$.
(Note that individuals may self and individuals chosen to die may also reproduce,
but in a large population these details should be unimportant.)

@@

The infinitesimal model is a powerful and tractable model of trait inheritance,
but is polygenic to a fault,
excluding the possibility of loci of large effect
(that are often seen in practice).
In this paper,
we have looked at the possibility of using a broader range of central limit theorems
to extend the infinitesimal model to traits for which 
effect size distributions fall in the domain of attraction of the $\alpha$-stable distributions
(i.e., a larger proportion of variance
is explained by a smaller number of loci).
Indeed, we found evidence that this is true of many real traits,
although our relatively uncritical use of GWAS estimates makes this evidence suggestive at best.
Next, we show that in fact the infinitesimal model \emph{cannot} describe non-Gaussian distributions
\comment{XXX TODO}.
A recurring theme in the rest of the paper is
that just as the infinitesimal model is useful precisely because it ignores the genetic details,
it cannot apply once some genetic details are important
(i.e., there are loci of large effect).
Also, we show that removing big effects and using the infinitesimal model for the remainder is good \comment{todo incorporate this}.

>>>>

@@

We should now discuss what this counter-intuitive result says and does not say.
The proposition says, roughly, that if the parental alleles are unlinked and independently chosen,
and meiotic segregation is fair,
then independence of Mendelian sampling term from midparent value
\emph{implies} a joint Gaussian distribution for the two.
We have not assumed anything about the distribution of the trait in the population:
rather, we have showed that any model of this sort
that assumes independence of Mendelian sampling term and midparent value
must also, by logical necessity, have a Gaussian distribution for the two.
In other words,
since models can be easily set up for which the distribution of Mendelian sampling terms
is not Gaussian,
the implication of the proposition
is that for such models, independence of the Mendelian sampling term
is not likely a good assumption. \revpoint{1}{7}
Note that the proof does not depend on independence of the $X_\ell$:
indeed, alleles may be inherited together,
although in practice this would quickly create dependencies between the effects
of alleles at such linked loci. \revpoint{2}{5}
Also note that it is \emph{not} usually true that the components --
for instance, $U_M^{[1]}$ and $U_M^{[2]}$ --
are independent of each other.
Finally, note that although they may not be independent,
the Mendelian sampling term $R_M$ and the midparent value $\bar Z_M$
\emph{are} always uncorrelated, since $Z_M$ and $V_M$ are exchangeable.

@@

%%%%%%%%%%%%%%%%%%%%%%
\section{Abnormal quantitative genetics?}
    \label{sec:abnormal}

@@

To summarize, in this section we will uncritically assume that \llabel{clarification3}
the independence assumption of the infinitesimal model holds,
but with an arbitrary distribution for the Mendelian sampling term,
and ask which population trait distributions are possible.
To do this, we work at a higher level,
ignoring the genetic basis of the trait
\citep[and certainly not using the specific set-up of][]{barton2017infinitesimal}.

Concretely, consider a Moran process where an individual whose trait value is $Z$ dies at rate $\mu(Z)$
and is replaced by the offspring of two randomly chosen individuals,
i.e., a new individual with trait \llabel{offspring_eqn}
\begin{align*}
  \frac{Z^{1} +Z^{2}}{2} + R ,
\end{align*}
where $Z^{1}$ and $Z^{2}$ are independent draws from the empirical population distribution
and $R$ is an independent draw from the Mendelian sampling distribution
(independent of $Z^{1}$ and $Z^{2}$, with distribution to be specified). 
(Note that mutation might enter into $R$, but as the underlying genetic basis is not specified,
we do not attempt to disambiguate the various possible contributions.) \llabel{mutation_note}
Mutation-selection balance demands that that
the distribution of individuals removed by death
and the distribution of individuals added by birth are equal,
\ie that $(Z^{1} +Z^{2})/2 + R$ is equal in distribution
to a $\mu$-weighted choice of $Z$.
% In other words, for all bounded and continuous functions $f$,
% \begin{equation} \label{eqn:MSB_condition}
%     \E\left[ f\left(\frac{Z^{1} +Z^{2}}{2} + R \right) \right] = \frac{\E\left[ f(Z) \mu(Z) \right]}{\E[\mu(Z)]},
% \end{equation}
% where the expectation is with respect to the joint law of the population empirical distribution (the law of $Z$, $Z^{1}$ and $Z^{2}$), and $R$.
% 
% Since the set of functions $\mathcal{S} = \{e^{i \theta x} : \theta \in \R\}$ is separating (see \eg \S 3.4 in \cite{Ethier+Kurtz1986}), it suffices to show that \eqref{eqn:MSB_condition} holds for $f \in \mathcal{S}$, \ie
If the population is large enough,
we can treat the trait distribution as changing deterministically.
Taking the characteristic function of both these distributions,
deterministic mutation-selection balance is therefore equivalent to
\begin{align} \label{eqn:MSB_CF}
    \frac{\E\left[ e^{i \theta Z}\mu(Z) \right]}{\E[\mu(Z)]}
    =
    \E\left[ e^{i\theta\left(\frac{Z^{1} +Z^{2}}{2} + R \right)}\right] .
\end{align}
Now, we assumed that $Z^{1}$, $Z^{2}$, and $R$ are independent, so we can write \eqref{eqn:MSB_CF} as 
\begin{align*}
    \frac{\E\left[ e^{i\theta Z} \mu(Z) \right]}{\E[\mu(Z)]} &= \E\left[ e^{i\theta\left(\frac{Z^{1} +Z^{2}}{2} + R \right)}\right]\\
	% &= \E\left[ e^{i\frac{\theta}{2} Z^{1}}e^{i\frac{\theta}{2} Z^{2}}e^{\i\theta R}\right]\\
	&= \E\left[e^{i\frac{\theta}{2} Z^{1}}\right]\E\left[e^{i\frac{\theta}{2} Z^{2}}\right]\E\left[e^{i\theta R}\right]\\
	&= \phi\left(\frac{\theta}{2}\right)^{2} \Phi(\theta),
\end{align*}
where
$ \phi(\theta) = \mathbb{E}\left[e^{i\theta Z^{1}}\right] = \mathbb{E}\left[e^{i\theta Z^{2}}\right] $
and
$ \Phi(\theta) = \mathbb{E}\left[e^{i\theta R}\right] $
are the characteristic functions of $Z^{j}$ and $R$, respectively. 
In what follows, we will explore some non-Gaussian solutions $\phi(\theta)$ to equation \eqref{eqn:MSB_CF}:

@@

Since $\varphi(\theta)$ is a characteristic function, it has the Hermitian property: $\phi(-\theta) = \overline{\phi(\theta)}$, and thus $\psi(-\theta) = \overline{\psi(\theta)}$ and $\alpha(-\theta) = \overline{\alpha(\theta)}$.  In particular, if one (and by extension both) limits exist, we must have $\alpha'(0-) = \overline{\alpha'(0+)}$.  In this case, setting $-\gamma + i m = \alpha'(0+)$, we have
\[
	\alpha(\theta) = \begin{cases} 
		i m\theta - \gamma \theta & \text{if $\theta \geq 0$, and}\\
		i m\theta + \gamma \theta & \text{if $\theta < 0$}.
	\end{cases}
\]
If $\gamma > 0$, then we recognize $e^{\psi(\theta)} = e^{im \theta -\gamma|\theta|}$
as the characteristic function of a Cauchy distribution with median 0 and median absolute deviation $\gamma$
(\ie, the canonical $\alpha$-stable distribution with $\alpha=1$), \llabel{cauchy_note}
whereas if $\gamma = 0$, then $e^{\psi(\theta)} = e^{im \theta}$ is the Fourier transform of a Dirac mass at $m$, \ie the characteristic function for a monomorphic population with all individuals having trait value equal to $m$.

% This might seem a bit roundabout, but the point is that we can prove that $e^{\psi(\theta)}$ is -- in this case -- a characteristic function, so we don't need to lose generality by assuming that it is one.  Our goal is to ask when $\lim_{n \to \infty} \varphi\left(\frac{\theta}{2^{n}}\right)^{2^{n}}\prod_{k=0}^{n-1}\Phi\left(\frac{\theta}{2^{k}}\right)^{2^{k}}$ is a valid characteristic function, and to see what it can be.  
To exclude the case $\gamma < 0$, we first observe that if, as we assume, $\varphi(\theta)$ is the characteristic function of some random variable, say $X$, then $\varphi_{n}(\theta) = \varphi\left(\frac{\theta}{2^{n}}\right)^{2^{n}} = e^{2^{n}\psi\left(\frac{\theta}{2^{n}}\right)}$ is the characteristic function of $2^{-n} \sum_{i = 1}^{2^{n}} X_{i}$, where $X_{1},\ldots,X_{2^{n}}$ are i.i.d.\ copies of $X$; now, L\'evy's continuity theorem (see \eg Theorem 2.3.4 in \cite{Durrett2005}) tells us that if (i) $\phi_{n}(\theta)$ has a point-wise limit, say $\phi_{\infty}(\theta)$, and (ii) $\phi_{\infty}(\theta)$ is continuous at 0, then $\phi_{\infty}(\theta)$ is the characteristic function of \emph{some} random variable; in particular, if $\alpha(\theta)$ exists and is bounded (\eg if the left and right-hand side derivatives exist, as above), then $\psi(\theta) = \alpha(\theta)\theta$ is continuous at 0, and hence so is $e^{\psi(\theta)}$.  Thus, in this case $e^{\psi(\theta)}$ is itself a characteristic function.  Moreover, being a characteristic function, $e^{\psi(\theta)}$ must satisfy $|e^{\psi(\theta)}| = e^{\Re \psi(\theta)} \leq 1$, whence $\gamma \geq 0$.

@@

More generally, \revpoint{2}{9}
the trait distribution in the population will converge as time proceeds
if the noise is a mixture of components with finite variance and stable laws as above,
whereas the population distribution will be a mixture of a (possibly degenerate) Cauchy distribution and such noise terms. Note that in the presence of noise, a pure Cauchy-distributed solution is \emph{not} possible in the neutral case.

@@

\section{The difficulty with an abnormal quantitative genetics}
    \label{sec:difficulty}

@@

%%%%%%%%%%%%%%%%%%%%%%
\section{Simulations}
    \label{sec:simulation}

In simulation we can easily include realistic recombination (instead of unlinked loci) and selection.
We used SLiM v4 \citep{haller2022slim4}
to simulate a discrete-time approximation to the continuous-time Moran model described above
as follows.
Individuals are diploid, hermaphroditic, and sexual;
the genome is of length $10^8$bp with a uniform recombination rate of $10^{-8}$ crossovers per bp;
mutations occur at a rate of $10^{-9}$ per bp. \llabel{mutation_rate}
Each new mutation is independently assigned an ``effect''
drawn from the ``effect size distribution'' (and will be either Gaussian or Cauchy).
The trait of each individual is determined additively
by summing the effects of all mutations they carry across both chromosomes.
Let $\mu(z)$ be the death rate of an individual with trait $z$,
and let $dt$ be a small constant (we took $dt=0.01$).
In all plots, one time unit is approximately one generation.
Then, at each time step
each individual dies with probability $1 - \exp(-dt \mu(z))$;
if there are $k$ such individuals chosen to die in a given time step,
then we choose $k$ individuals uniformly and without replacement
to produce new offspring;
for each such reproduction event the parent chooses a mate uniformly at random from the population.
This maintains the population at a fixed size, $N$.
(Note that individuals may self and individuals chosen to die may also reproduce,
but in a large population these details should be unimportant.)

@@

The infinitesimal model is a powerful and tractable model of trait inheritance,
but is polygenic to a fault,
excluding the possibility of loci of large effect
(that are often seen in practice).
In this paper,
we have looked at the possibility of using a broader range of Central Limit Theorems
to extend the infinitesimal model to traits for which 
effect size distributions fall in the domain of attraction of the $\alpha$-stable distributions
(for which a larger proportion of variance
would be explained by a smaller number of loci).
Indeed, we found evidence that this is true of many real traits,
although our relatively uncritical use of GWAS estimates makes this evidence suggestive at best.
Next, we show that in fact the infinitesimal model \emph{cannot} describe non-Gaussian distributions
(\ie, non-Gaussian deviation of offspring trait from midparent value)
if the traits are determined additively from independent loci
(for a precise statement, see Proposition~\ref{prop:parental_contribs}).
The problem is large-effect alleles:
as described in Section~\ref{sec:difficulty},
if large-effect alleles are present, then naturally parental trait values give information about parental genotypes,
and hence about the distribution of offspring trait deviations.
This also suggests that the infinitesimal model might be a good approximation
once the largest alleles are removed,
an idea we find support for in theory (Section~\ref{sec:difficulty}) and simulation (Section~\ref{sec:simulation}).
Despite having spent a fair bit of time describing why
the infinitesimal model cannot strictly apply 
to an additive model with non-Gaussian effect size distributions,
we still found it useful to work out some of the consequences if we took it seriously:
the calculations in Section~\ref{sec:abnormal}
suggested a tractable form of stabilizing selection that we used in simulations,
and revealed an intriguing (if not strongly biologically motivated)
model in which blending inheritance retains heritable variance.

For simplicity, we have focused on the $\alpha=1$ case (which includes the Cauchy distribution).
However, examination of Figure~\ref{fig:exponent_hist} suggests that $\alpha=3/2$
would be a more natural choice for an effect size distribution.
(One could use the Holtsmark distribution,
or Student's $t$ with 1.5 degrees of freedom,
which has the same tail behavior.)
This would be particularly interesting to investigate further,
because such distributions are not so extreme as the Cauchy,
as the largest out of $M$ observations grows only as $M^{2/3}$ --
so, in a trait determined by $M$ loci,
the largest-effect allele will contribute only about $1/M^{1/3}$ of the typical trait value
(and hence the largest effects are less important for more polygenic traits).
